%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Research Assistant Professor} % Job title
    {Kansas State University} % Organization
    {Manhattan, KS} % Location
    {Apr. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Phenomics co-lead on Innovation Lab for Crop Improvement, focused on modernizing breeding data collection}
        \item {Lead development of mobile apps used by 4,000+ plant scientists}
        \item {Collaborate with external teams to improve breeding data management}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Postdoctoral Fellow} % Job title
    {Kansas State University} % Organization
    {Manhattan, KS} % Location
    {Dec. 2016 - Mar. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed mobile applications for phenotypic data collection}
        \item {Led training workshops in Nigeria, Uganda, Tanzania, Bangladesh, Nepal, and India for PhenoApps that trained 150+ scientists}
        \item {Developed project website and training modules: \href{www.PhenoApps.org}{\textit{PhenoApps.org}}}
        \item {Managed a team of three developers}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Kansas State University} % Organization
    {Manhattan, KS} % Location
    {Jul. 2011 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized historical data (22 years; 939 entries; 100k plots) to validate genomic selection as a  tool for regional plant breeding}
        \item {Organized and managed multi-environment field experiments to estimate genetic gain over the last 20 years}
        \item {Developed a marker technology for targeted allele genotyping}
        \item {Designed and developed Field Book mobile app for plant scientists}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant Plant Breeder} % Job title
    {High Plains Crop Development} % Organization
    {Torrington, WY} % Location
    {May 2006 - Jul. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planted, harvested, crossed, and selected canola varieties}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {University of Wyoming (Dr. Dan Wall Lab)} % Organization
    {Laramie, WY} % Location
    {Jan. 2010 - May 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Characterized NTRC-like activator mutants in \textit{Myxococcus xanthus}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {University of Wyoming (Dr. Peter Thorsness Lab)} % Organization
    {Laramie, WY} % Location
    {Jan. 2009 - May 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generated and characterized BAX mutants in \textit{Saccharomyces cerevisiae}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
